We will calculate this using the comparison theorem and the standard affine
cover $\mathcal{U} = \set{U_i = D_+(X_i)\given 0\leq i\leq r}$. Furthermore,
we will be calculating the cohomology of $\mathcal{F}\coloneqq \bigoplus_{n \in \mathbb{Z}} \mathcal{O}_X(n)$
(this is not coherent, but it is quasicoherent)
and then we will be done because cohomology commutes with coproducts (this must
be checked).

The key point is the following: recall that the transition map for $\mathcal{O}_X(1)$
from $U_i$ to $U_j$ is $X_i/X_j$, and so the transition maps for $\mathcal{O}_X(m)$
are $X_i^m/X_j^m$. For $I \subseteq \set{0, \ldots r}$, we have $U_I = \cap_{i \in I} D_+(X_i) = D_+(X_I)$,
where $X_i\coloneqq \prod_{i \in I} X_i$.

Thus $\Gamma(U_I, \mathcal{O}_{\mathbb{P}^r}\cong S_{(X_I)}$. We will identify
$\Gamma(U_I, \mathcal{O}_X(m))$ with the $k$-subspace of $S_{X_I}$ spanned by
Laurent monomials of degree $m$, i.e., monomials of the form
$X_0^{a_0}\cdots X_r^{a_r}$ with $\sum a_i = n$ and $a_i < 0\implies i \in I$.

Given such a monomial $M$, using the trivialization on $U_i$, we will
identify the section of $\mathcal{O}_X(m)$ defined by $M$ with
$M/X_i^m \in \Gamma(U_I, \mathcal{O}_{\mathbb{P}^r}$ (with $i \in I$).

If $i, j \in I$, then note
\[ \frac{M}{X_i^m}\cdot \frac{X_i^m}{X_j^m} = \frac{M}{X_j^m}. \]
Thus we have a canonical identification of $\Gamma(U_I, \mathcal{O}_{\mathbb{P}^r}(m))$
with the space spanned by Laurent monomials of degree $m$.

Thus $\Gamma(U_I, \mathcal{F})$ can be identified with $S_{X_I}$.

Now we have a Cech complex $C^\bullet(\mathcal{U}, \mathcal{F})$ which looks like
\[\begin{tikzcd}
	\prod_{0\leq i_0\leq r}S_{X_{i_0}} \ar[r, "d_0"] & \prod_{0\leq i_0\leq i_1\leq r} S_{X_{i_0}X_{i_1}}\ar[r] & \cdots\ar[r, "d_{r-1}"] & S_{X_0\cdots X_r}.
\end{tikzcd}\]

Note that $H^0(X, \mathcal{F}) = \ker d_0$. Note also that all modules in the Cech
complex are sub-$S$-modules of $S_{X_0\cdots X_r}$.
We have
\[ d_0((f_i)_{i \in\set{0, \ldots, r}}) = (f_j - f_i)_{0\leq i<j\leq r}. \]
Thus if $(f_i)_{0\leq i\leq r} \in \ker d_0$ we actually have $f_i = f_j$ for all $i$.

Thus $f_i, f_j \in S$ since otherwise $f_i$ involves a negative power of
$X_i$, which can't occur in $f_j$, or vice versa. Thus $_i = f$ for all $i$
with $f \in S$, and hence $\ker d_0\cong S$. Thus $H^0(X, \mathcal{F}) = S$
preserving degrees, so $H^0(X, Ocal_X(m)) = S_m$.

Now consider
\[ d_{r-1}\colon \prod_{0\leq k\leq r} S_{X_0\cdots \widehat{X_k}\cdots X_r} \to S_{X_0\cdots X_r}. \]
Note $S_{X_0\cdots X_r}$ is the $k$-vector space with basis
$\prod_{i = 0}^r X_i^{a_i}$, where the $a_i \in \mathbb{Z}$ and the image of
$d_{r-1}$ is spanned by monomials of the form
$\prod_{i = 0}^r X_i^{a_i}$ with at least one $a_i\geq 0$. Thus a basis
for $\coker d_{r-1}$ is given by
\[ \set{\prod_{i =0}^r X_ia_i\given a_i\leq -1 \forall i}. \]
In particular, $H^r(X, \mathcal{O}_X(-r-1))$ is generated by
$X_0^{-1}\cdots X_r^{-1}$, and thus $H^r(X, \mathcal{O}_X(r-1))\cong k$.

For the perfect pairing, note that $H^0(\mathbb{P}^r, \mathcal{O}_{\mathbb{P}^r}(n)) = 0$
for $n < 0$, as $S_n = 0$ for $n < 0$, and $H^r(\mathbb{P}^r, \mathcal{O}_{\mathbb{P}^r}(-n-r-1)) = 0$
for $n < 0$ as there are no monomials with only negative exponents of degree
greater than $-r-1$, and so there is nothing to check in this case.

If $n\geq 0$, we have a basis
\[ \set{\prod_i X_i^{m_i}\given\sum m_i = n, m_i\geq 0} \]
for $H^r(X, \mathcal{O}_X(n))$ and a basis
\[ \set{\prod_i X_i^{\ell_i}\given \sum \ell_i = -n-r-1, \ell_i\leq -1} \]
for $H^r(X, \mathcal{O}_X(-n-r-1))$. The perfect pairing is given by
\[ (X_0^{m_0}\cdots X_r^{m_r})\cdots(X_0^{\ell_0}\cdots X_r^{\ell_r}) = X_0^{m_0+\ell_0}\cdots X_r^{m_r+\ell_r}, \]
where we interpret the result as $0$ if $m_i+\ell_i \leq 0$ for any $i$. Indeed,
this gives a pairing
\[ H^0(X, \mathcal{O}_X(n))\times H^r(X, \mathcal{O}_X(-n-r-1))\to H^r(X, \mathcal{O}_X(-r-1)) = k(X_0\cdots X_r)^{-1} \]
and it is easy to check that it is perfect.

It remains to show that $H^i(X, \mathcal{O}_X(m)) = 0$ for $0 < i < r$. The proof
will be by induction on $r$.

In the base case $r=1$ the statement is vacuous. For the induction step, if
we localize $C^\bullet(\mathcal{U}, \mathcal{F})$ at $X_r$ as graded $S$-modules,
we get a Cech complex which calculates the cohomology groups $H^i(\mathcal{U}_r, \mathcal{F}|_{\mathcal{U}_r})$
(calculate using the Cech cover $\mathcal{U}' = \set{U_i\cap U_r\given 0\leq i\leq r}$).
But $U_r\cong \mathbb{A}^r_k$, and Cech cohomology can also be calulated via
the cover $\set{U_r}$, so $H^i(\mathcal{U}_r, \mathcal{F}|_{\mathcal{U}_r}) = 0$ for
all $i$\footnote{Observe that this implies that if $\mathcal{F}$ is any quasicoherent
sheaf on an affine scheme $X$, then $H^i(X, \mathcal{F}) = 0$ for all $i > 0$. But this
is not really a proof, because the proof of the comparison theorem uses this fact. Actually,
vanishing cohomology for any quasicoherent sheaf in positive degree characterises affine
schemes.}

Now localizing at $X_r$ is an exact functor, so
\[ H^i(C^\bullet(\mathcal{U}, \mathcal{F})_{X_r}) = H^i(C^\bullet(\mathcal{U}, \mathcal{F}))_{X_r}, \]
so thus, $H^i(X, \mathcal{F}_{X_r} = H^i(\mathcal{U}_r, \mathcal{F}|_{\mathcal{U}_r}) = 0$ for $i > 0$.
For this to be the case, every element of $H^i(X, \mathcal{F})$ must be annihilated by some
power of $X_r$.

Now let $H = V(X_r) \subseteq \mathbb{P}^r$. Thinking of this as a closed subscheme,
we may write $H = \Proj S/(X_r) = \Proj k[X_0, \ldots, X_{r-1}] = \mathbb{P}^{r-1}$.

We have a surjective map $\mathcal{O}_{\mathbb{P}^r} \to i_*\mathcal{O}_H$,
where $i\colon H\to \mathbb{P}^r$ is the inclusion. Because $H$ is defined
locally by a single equation, the kernel of $\mathcal{O}_{\mathbb{P}^r}\to i_*\mathcal{O}_H$
is a line bundle. Note that this kernel is the ideal sheaf corresponding to $H$.
On $U_i = \Spec S_{(X_i)}$, this kernel is generated by $X_r/X_i$ and hence the
transition maps for the ideal sheaf $\mathcal{I}_{H/X}$ are given by
\[\begin{tikzcd}
	\mathcal{O}_{U_i}|_{U_i\cap U_j}\ar[r, "X_r/X_i"] & \mathcal{I}_{H/X}|_{U_i\cap U_j} & \mathcal{O}_{U_j}|_{U_i\cap U_j}\ar[l, "X_r/X_j"]
\end{tikzcd}\]
the first map followed by the inverse of the second is given by $\frac{X_r}{X_i}\cdot\frac{X_j}{X_r} = \frac{X_j}{X_i}$,
i.e., the inverse of the transition map of $\mathcal{O}_{\mathbb{P}^r}(1)$, so we conclude that
$\mathcal{I}_{H/X} \cong \mathcal{O}_{\mathbb{P}^r}(-1) = \mathcal{O}_{\mathbb{P}^r}(-H)$.

A remark: In general, given an effective Cartier divisor $D = \set{(U_i, f_i)}$, $f_i \in \mathcal{O}_X(U_i)$,
$D$ defines a closed subscheme of $X$ whose ideal in $U_i$ is generated by $f_i$. This
coincides with the line bundles $\mathcal{O}_X(-D)$.

The upshot of all of this is that we have an exact sequence
\[\begin{tikzcd}
	0\ar[r] & \mathcal{O}_{\mathbb{P}^r}(-1)\ar[r, "\cdot X_r"] & \mathcal{O}_{\mathbb{P}^r}\ar[r] & i_*\mathcal{O}_H\ar[r] & 0,
\end{tikzcd}\]
where the multiplication by $X_r$ makes sense: on $U_i$, it means multiplying by $X_r/X_i$, recalling
that $X_r$ corresponds to the section $X_r/X_i$ of $\mathcal{O}_{\mathbb{P}^r}(1)$ on $U_i$.

We can tensor the exact sequence with $\mathcal{O}_{\mathbb{P}^r}(n)$. This is still exact,
so we get
\[\begin{tikzcd}
	0\ar[r] & \mathcal{O}_{\mathbb{P}^r}(n-1)\ar[r] & \mathcal{O}_{\mathbb{P}^r}(n) \ar[r] & i_*\mathcal{O}_H(n)\ar[r] & 0.
\end{tikzcd}\]
Exactness on the left follows since $\mathcal{O}_{\mathbb{P}^n}(n)$ is locally free, haence flat
(or, more simply, on $U_i$ we have $\mathcal{O}_{\mathbb{P}^r}(n)\cong \mathcal{O}_{U_i}$, so tensoring with
$\mathcal{O}_{U_i}$ doesn't do anything). Note also that $(i_*\mathcal{O}_H)\tensor_{\mathcal{O}_{\mathbb{P}^r}}\mathcal{O}_{\mathbb{P}^r}(n)\cong i_*(\mathcal{O}_H(n))$,
which can be seen by considering transition maps. Frequently, we will drop the $i_*$ when
dealing with sheaves on a closed subscheme, i.e., if $\mathcal{F}$ is a sheaf on $H$ we
often write $\mathcal{F}$ for $i_*\mathcal{F}$ (where $(i_*\mathcal{F})(U) = \mathcal{F}(U\cap H)$).

Thus we have an exact sequence
\[\begin{tikzcd}
	0\ar[r] & \mathcal{O}_{\mathbb{P}^r}(-n-1)\ar[r, "\cdot X_r"] & \mathcal{O}_\mathbb{P}^r(n)\ar[r] * \mathcal{O}_H(n)\ar[r] & 0.
\end{tikzcd}\]
Summing over all $n$, we get
\[\begin{tikzcd}
	0\ar[r] & \mathcal{F}(-1)\ar[r] & \mathcal{F}\ar[r] & \mathcal{F}_H\ar[r] & 0,
\end{tikzcd}\]
where $\mathcal{F}(-1)\coloneqq \mathcal{F}\tensor \mathcal{O}_{\mathbb{P}^r}(-1)$. and
$\mathcal{F}_H = \bigoplus_{n \in\mathbb{Z}} \mathcal{O}_H(n)$.

By the induction hypothesis, we have $H^i(\mathbb{P}^r, \mathcal{F}_H) = 0$ for
$0 < i < r-1$, where we have used that $H^i(\mathbb{P}^r, \mathcal{F}_H) = H^i(H, \mathcal{F}_H)$
because the Cech complexes calculating them are the same, i.e., if we use
$\mathcal{U} = \set{U_i}$ or $\mathcal{U}_H = \set{U_i \cap H}$. This is a general fact:
if $i\colon Y\to X$ is a closed immersion and $\mathcal{F}$ is a sheaf on $Y$, then
$H^p(X, i_*\mathcal{F}) = H^p(Y, \mathcal{F})$.


So if $1 < i < r-1$, we get a piece of the long exact cohomology sequence
\[ 0 = H^{i-1}(\mathbb{P}^r, \mathcal{F}_H)\to H^i(\mathbb{P}^r, \mathcal{F}(-1))\to H^i(\mathbb{P}^r, \mathcal{F}) \to H^i(\mathbb{P}^r, \mathcal{F}H) = 0, \]
and so $(\cdot X_r)\colon H^i(\mathbb{P}^r, \mathcal{F}(-1))\to H^i(\mathbb{P}^r, \mathcal{F})$ is
an isomorphism. But note that $H^i(\mathbb{P}^r, \mathcal{F}(-1)) = H^i(\mathbb{P}^r, \mathcal{F})$ as
non-graded $S$-modules. But we know that every element of $H^i(\mathbb{P}^r, \mathcal{F})$ is
annihilated by some power of $X_r$. Thus, we must have $H^i(\mathbb{p}^r, \mathcal{F}) = 0$ for
$1 < i < r-1$.

It remains to deal with the cases $i = 1$ and $i = r-1$

For $i = 1$ we have
\[ 0\to H^0(\mathbb{P}^r, \mathcal{F}(-1))\to H^0(\mathbb{P}^n, \mathcal{F})\to H^0(\mathbb{P}^r, \mathcal{F}_H)\to H^1(\mathbb{P}^r, \mathcal{F}(-1))\to H^1(\mathbb{P}^r, \mathcal{F})\to 0. \]
This first two non-zero terms are just $S$, but with different gradings. The first
one is the $S$-module $S(-1)$, i.e., we have $S(-1)_d = S_{d-1}$. The third term is $S/(X_r)$,
and the map $S\to S/(X_r)$ is surjective. But then the map after that is zero, which in turn
means that the map $(\cdot X_r)\colon H^1(\mathbb{P}^r, \mathcal{F}(-1))\to H^1(\mathbb{P}^r, \mathcal{F})$
is injective, and hence, as before, $H^1(\mathbb{P}^r, \mathcal{F}) = 0$.

For $i = r-1$, we get
\[ H^{r-1}(\mathbb{P}^r, \mathcal{F}_H)\to H^r(\mathbb{P}^r, \mathcal{F}(-1))\to H^r(\mathbb{P}^r, \mathcal{F})\to H^r(\mathbb{P}^r, \mathcal{F}_H) = 0, \]
where the second map is again multiplication by $X_r$.

By our calculation, the kernel of $(\cdot X_r)$ is generated by
\[ \set{X_0^{\ell_0}\cdots X_r^{\ell_r}\given \forall i\colon \ell_i\leq -1, \ell_r = -1}. \]
This is identified with $H^{r-1}(\mathbb{P}^r, \mathcal{F}_H)$, and so the first
map is injective (this should be checked, which involves understanding the Cech
cohomology connecting maps) and we conclude that
\[ H^{r-1}(\mathbb{P}^r, \mathcal{F}(-1))\stackrel{\cdot X_r}{\longrightarrow} H^{r-1}(\mathbb{P}^r, \mathcal{F}) \]
is surjective. Thus multiplucation by $X_r$ is an isomorphism, and we conclude as before
that $H^{r-1}(\mathbb{P}^r, \mathcal{F}) = 0$.
