\begin{enumerate}
	\item Let $k$ be a field. Then $\Spec k = (\set{0}, k)$.

		What does giving a morphism $f\colon \Spec k\to X$ a scheme mean?

		First, we need to choose a point $x \in X$, the image of $f$. Second,
		we get a local ring homomorphism
		\[ f^\#_x\colon \mathcal{O}_{X, x} \to \mathcal{O}_{\Spec k, 0} \cong k, \]
		i.e., $(f_x^\#)^{-1}(0) = m_x \subseteq \mathcal{O}_{X, x}$, the maximal
		ideal of $\mathcal{O}_{X, x}$. Thus we get a factorization
		$f^\#_x\colon \mathcal{O}_{X, x}\to \mathcal{O}_{X, x}/m_x \to k$.
		The middle quotient is a field denoted as $\kappa(x)$, the residue field
		of $X$ at $x$.

		Thus $f$ induces an inclusion $\kappa(x) \to k$.

		Conversely, given an inclusion $\iota\colon\kappa(x)\to k$ we get a morphism of
		schemes $\Spec k\to X$ by defining $f(0) = x$ and
		$f^\#\colon \mathcal{O}_X\to f_*k$ by defining $s\mapsto \iota(s(x)) \in k$,
		where $s(x)$ means taking the stalk of $s$ at $x$.

		Moral: Giving a morphism $f\colon \Spec k\to X$ is equivalent to giving
		a point $x \in X$ and an inclusion $\kappa(x)\to k$.

		Note: If $X = \Spec A$, then giving a morphism $\Spec k \to \Spec A$ is
		equivalent to giving a homomorphism $A\to k$, which we viewed at the
		beginning of the course as a \enquote{$k$-valued point} on $\Spec A$.
	\item What does giving a morphism $X\to \Spec k$ mean? The continuous map
		$X \to \Spec k$ does not carry any information, since $\Spec k$ is
		a singleton space. We also have a map
		\[ f^\#\colon k \cong \mathcal{O}_{\Spec k} f_*\mathcal{O}_X, \]
		i.e., a map $k\to \Gamma(\Spec k, f_*\mathcal{O}_X) = \Gamma(X, \mathcal{O}_X)$,
		i.e., $\Gamma(X, \mathcal{O}_X)$ carries a $k$-algebra structure.

		Notice that this induces $k$-algebra structures on $\mathcal{O}_X(U)$
		for all open sets $U$ via the composite
		\[ k \longrightarrow \mathcal{O}_X(X) \stackrel{\rho}\longrightarrow \mathcal{O}_X(U), \]
		and similarly all stalks $\mathcal{O}_{X, p}$ are also $k$-algebras.

		In this situation we say that $X$ is a scheme (defined) over $k$.
	\item Consider $A = k[X_1, \ldots, X_n]/I$ with $I = \sqrt{I}$. Then
		$\Spec A$ is a replacement for $V(I) \subseteq \mathbb{A}^n_k$, viewing
		$\Spec A$ as a scheme over $k$.

		If $k \subseteq k'$ is a field extension, a $k'$-valued point of $X/k$ is
		a commutative diagram
		\[\begin{tikzcd}
			\Spec k' \ar[r]\ar[dr] & X\ar[d]\\
			& \Spec k,
		\end{tikzcd}\]
		which has the dual
		\[\begin{tikzcd}
			k' & A\ar[l]\\
			& k\ar[u]\ar[ul],
		\end{tikzcd}\]
		so the top arrow is a homomorphism of  $k$-algebras.

		We write $X(k')$ for the set of such morphisms.
\end{enumerate}
