For (a), we just need to notice that $F$ is fully faithful, so it induces a
bijection between the sets of morphisms $S\to S$ and $FS \to FS$. Since $S$ is
determined up to isomorphism by having exactly three endomorphisms, the claim
follows.

The proof of (b) is entirely analogous to the proof of 2.13(ii).

For (c), write $FS = \set{\tilde{0}, \tilde{1}}$ such that $\set{\tilde{1}}$ is open.
Suppose that $\alpha_S$ is not continuous. Then $\alpha_S$ must send
$0 \mapsto \tilde{1}$ and $1\mapsto \tilde{0}$. Now let $U \subseteq X$ be an
open set of some topological space in $\mathcal{C}$. Consider the map $g\colon X\to S$ which sends $x \in X$ to $1$ if and only if
$x \in U$. This map is continuous. Define $f\coloneqq F^{-1}g$, then by naturality
we have
\[ (\alpha_{F^{-1}X})^{-1}(U) = \alpha_{F^{-1}X}^{-1}((UFf)^{-1}(\set{\tilde{1}})) = (Uf)^{-1}((\alpha_S)^{-1}(\tilde{1})) = (Uf)^{-1}(\set{0}). \]
Since $f$ is continuous, the right hand side is closed. Hence the preimage under $\alpha_{F^{-1}X}$ of an open
set is closed. In analogous fashion and using the fact that $F^{-1}$ is also an automorphism
(noting that $\alpha^{-1}$ must be the unique natural isomorphism $U\to UF^{-1}$),
we find that for any space  $X$ in $\mathcal{C}$ we have
\begin{itemize}
	\item the preimage under $\alpha_X$ of an open set is closed,
	\item the preimage under $\alpha_X$ of a closed set is open,
	\item the image under $\alpha_X$ of an open set is closed,
	\item the image under $\alpha_X$ of a closed set is open.
\end{itemize}
Now let $X$ be a space in $\mathcal{C}$ and a collection $U_i$ closed sets such
that $\bigcup U_i$ is not closed. We have
\[ \alpha_X^{-1}(\bigcup U_i) = \bigcup \alpha_X^{-1}(U_i), \]
where the left hand side is not open, since otherwise $\bigcup U_i$ would be closed,
but the right hand side is open, since $\alpha_X^{-1}(U_i)$ is open for every $i$.
This is a contradiction, so $\alpha_S$ is continuous.

For (d), we can now carry out the same calculation as above to find that
$\alpha_X$ and $\alpha_X^{-1}$ are continuous for every $X$, so $\alpha$ lifts to a natural isomorphism
$1_C\to F$, which must be unique since the forgetful functor $[\mathcal{C}, \mathcal{C}]\to [\mathsf{Set}, \mathsf{Set}]$
is faithful.
